---
title: "Numbers for cohort eligibility flowcharts"
format: html
editor: visual
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
    warning = F, message = F, echo=F,
  comment = '', fig.width = 6, fig.height = 6
)
library(tidyverse)


```

# Analysis cohort

```{r}
analysis_cohort_exclusions <-read_rds(here::here("projects/create_cohort/output/analysis_cohort_exclusions.rds"))

cohort<- analysis_cohort_exclusions # cohort= cohort

cohort_n <- sum(cohort$n)
cat(paste("Unique beneficiaries N =", cohort_n))
```

### Enrollment date Jan 1 2016

```{r}
exclusion <- "cohort_exclusion_cal_jan2016"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### No washout period (enrolled too late in 2019)

```{r}
exclusion <- "cohort_exclusion_cal_no_washout"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### No eligibility criteria

```{r}
exclusion <- "cohort_exclusion_cal_no_elig"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Unknown disability status

```{r}
exclusion <- "cohort_exclusion_cal_unknown_disability"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### State

```{r}
exclusion <- "cohort_exclusion_state"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Age

```{r}
exclusion <- "cohort_exclusion_age"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Pregnancy

```{r}
exclusion <- "cohort_exclusion_cal_pregnancy"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Dual enrollment

```{r}
# cohort <- cohort|> mutate(cohort_exclusion_dual = 
#                      cohort_exclusion_cal_dual + cohort_exclusion_cal_dual_elig,
#                      cohort_exclusion_dual = ifelse(cohort_exclusion_dual >= 1, 1, 0))

exclusion <- "cohort_exclusion_cal_dual"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Deaf or blind

```{r}
cohort <- cohort|> mutate(cohort_exclusion_db = 
                     cohort_exclusion_deaf + cohort_exclusion_blind + cohort_exclusion_cal_deafblind,
                     cohort_exclusion_db = ifelse(cohort_exclusion_db >= 1, 1, 0))

exclusion <- "cohort_exclusion_db"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Dementia

```{r}
exclusion <- "cohort_exclusion_cal_dementia"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Intellectual disabilities

```{r}
exclusion <- "cohort_exclusion_cal_itlcdsbl"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Schizophrenia

```{r}
exclusion <- "cohort_exclusion_cal_schiz"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Speech problems

```{r}
exclusion <- "cohort_exclusion_cal_speech"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Cerebral Palsy

```{r}
exclusion <- "cohort_exclusion_cal_cerpals"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Epilepsy

```{r}
exclusion <- "cohort_exclusion_cal_epilepsy"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Tuberculosis

```{r}
exclusion <- "cohort_exclusion_cal_tb"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Cancer

```{r}
exclusion <- "cohort_exclusion_cal_cancer"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### LTC

```{r}
exclusion <- "cohort_exclusion_cal_ltc"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Palliative care

```{r}
exclusion <- "cohort_exclusion_cal_pall"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Institutionalized

```{r}
exclusion <- "cohort_exclusion_cal_institution"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### OUD

```{r}
exclusion <- "cohort_exclusion_oud_cal"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

# Descriptive cohort

```{r}
desc_cohort_exclusions <-read_rds(here::here("projects/create_cohort/output/desc_cohort_exclusions.rds"))

cohort<- desc_cohort_exclusions # cohort= cohort
```

### No washout period (enrolled too late in 2019)

```{r}
exclusion <- "cohort_exclusion_cont_no_washout"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### No eligibility criteria

```{r}
exclusion <- "cohort_exclusion_cont_no_elig"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Unknown disability status

```{r}
exclusion <- "cohort_exclusion_cont_unknown_disability"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### State

```{r}
exclusion <- "cohort_exclusion_state"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Age

```{r}
exclusion <- "cohort_exclusion_age"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Pregnancy

```{r}
exclusion <- "cohort_exclusion_cont_pregnancy"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Dual enrollment

```{r}
exclusion <- "cohort_exclusion_cont_dual"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Deaf or blind

```{r}
cohort <- cohort|> mutate(cohort_exclusion_db = 
                     cohort_exclusion_deaf + cohort_exclusion_blind + cohort_exclusion_cont_deafblind,
                     cohort_exclusion_db = ifelse(cohort_exclusion_db >= 1, 1, 0))

exclusion <- "cohort_exclusion_db"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Dementia

```{r}
exclusion <- "cohort_exclusion_cont_dementia"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Intellectual disabilities

```{r}
exclusion <- "cohort_exclusion_cont_itlcdsbl"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Schizophrenia

```{r}
exclusion <- "cohort_exclusion_cont_schiz"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Speech problems

```{r}
exclusion <- "cohort_exclusion_cont_speech"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Cerebral Palsy

```{r}
exclusion <- "cohort_exclusion_cont_cerpals"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Epilepsy

```{r}
exclusion <- "cohort_exclusion_cont_epilepsy"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Tuberculosis

```{r}
exclusion <- "cohort_exclusion_cont_tb"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Cancer

```{r}
exclusion <- "cohort_exclusion_cont_cancer"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### LTC

```{r}
exclusion <- "cohort_exclusion_cont_ltc"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Palliative care

```{r}
exclusion <- "cohort_exclusion_cont_pall"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```

### Institutionalized

```{r}
exclusion <- "cohort_exclusion_cont_institution"

n_exclude <- cohort|>
    filter(.data[[exclusion]] == 1) |>
    pull(n) |>
    sum()
cat(paste("Excluded n =", n_exclude))

cohort<- cohort|>
    filter(.data[[exclusion]] == 0)

cohort_n <- sum(cohort$n)
cat(paste("New cohort N =", cohort_n))
```
